% ADD THIS HEADER TO ALL NEW CHAPTER FILES FOR SUBFILES SUPPORT

% Allow independent compilation of this section for efficiency
\documentclass[../CLthesis.tex]{subfiles}

% Add the graphics path for subfiles support
\graphicspath{{\subfix{../images/}}}

% END OF SUBFILES HEADER

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% START OF DOCUMENT: Every chapter can be compiled separately
\begin{document}
\phantomsection% to get the hyperlinks (and bookmarks in PDF) right for index, list of files, bibliography, etc.
\addcontentsline{toc}{chapter}{Abstract}

\begin{abstract}

    \begin{otherlanguage}{english}% Switch to English, in case the main language is not English

        \section*{Abstract}
        Computational hate speech research remains concentrated on English-language data, explicit lexical abuse, and binary classification --- leaving implicit, cross-lingual religious hostility structurally underexplored. This thesis investigates anti-Christian hate speech across Chinese, Japanese, and English online discourse, asking not only whether hostility can be detected, but \emph{who} is targeted, \emph{how} attacks are rhetorically constructed, and \emph{why} different communities sustain them.

        The thesis assembles a trilingual corpus of 63,265 texts and develops a modular \emph{who--how--why} analytical pipeline. Unsupervised BERTopic modelling with cross-lingual centroid alignment identifies 47 semantically coherent topics without imposing an English-centric taxonomy. Attack frames are classified using a ten-category taxonomy, and moral motivations are projected onto Moral Foundation axes extended with intergroup threat dimensions.

        The results reveal two structural regularities that binary detection alone cannot surface. First, attack frame selection is governed by the target's social category: clerical targets attract the Sexual Abuse Frame across all three languages, institutional targets attract Political Interference and Economic Exploitation, and collective identity labels attract Rhetorical Attack and Moral Accusation --- a cross-linguistically stable regularity. Second, English and East Asian communities inhabit fundamentally different moral architectures: English discourse aligns negatively across all five Moral Foundation axes, constituting broad ethical condemnation from within a shared normative framework, while Chinese and Japanese discourse aligns negatively on Symbolic and Realistic Threat axes, framing Christianity as a cultural and social danger rather than a moral transgressor.

        A trilingual annotated dataset and open-source pipeline are released at \url{https://github.com/notsofun/Master_Thesis}.

    \end{otherlanguage}
    %  A German Abstract is optional if there is an English one.
     \newpage \thispagestyle{empty}%if both languages need more than one page

    \begin{otherlanguage}{ngerman}% Switch to German for this part

        \section*{Zusammenfassung}

        Die computergestützte Hassrede-Forschung konzentriert sich nach wie vor auf englischsprachige Daten, expliziten lexikalischen Missbrauch und binäre Klassifikation --- eine Kombination, die implizite, mehrsprachige religiöse Feindseligkeit strukturell unterbelichtet lässt. Diese Arbeit untersucht anti-christliche Hassrede in chinesischen, japanischen und englischen Online-Diskursen und fragt nicht nur, ob Feindseligkeit erkannt werden kann, sondern \emph{wer} angegriffen wird, \emph{wie} Angriffe rhetorisch konstruiert werden und \emph{warum} verschiedene Sprachgemeinschaften sie aufrechterhalten.

        Es wird ein dreisprachiges Korpus aus 63.265 Texten zusammengestellt und eine modulare \emph{Wer-Wie-Warum}-Analysepipeline entwickelt. Unüberwachte BERTopic-Modellierung mit sprachübergreifender Zentroidsausrichtung identifiziert 47 semantisch kohärente Themen ohne englischzentrierte Taxonomievorgabe. Angriffsmuster werden anhand einer zehnkategorigen Taxonomie klassifiziert; moralische Motivationen werden auf Moral-Foundations-Achsen projiziert, die um intergruppale Bedrohungsdimensionen erweitert wurden.

        Die Ergebnisse offenbaren zwei strukturelle Regelmäßigkeiten. Erstens wird die Wahl des Angriffsrahmens durch die soziale Kategorie des Ziels bestimmt: Kleriker ziehen in allen drei Sprachen den Sexualmissbrauchs-Rahmen an; institutionell verankerte Ziele ziehen Politische Einflussnahme und Wirtschaftliche Ausbeutung an; kollektive Identitätslabels ziehen Rhetorischen Angriff und Moralische Anschuldigung an --- eine sprachübergreifend stabile Ziel-Rahmen-Regelmäßigkeit. Zweitens bewegen sich englischsprachige und ostasiatische Gemeinschaften in grundlegend verschiedenen moralischen Architekturen: Englischsprachiger Diskurs ist auf allen fünf klassischen Moral-Foundations-Achsen negativ ausgerichtet und konstituiert eine umfassende ethische Verurteilung; chinesischer und japanischer Diskurs hingegen weist negative Ausrichtungen auf den Symbolischen und Realistischen Bedrohungsachsen auf und rahmt das Christentum als kulturelle und soziale Gefahr, nicht als moralischen Akteur.

        Ein dreisprachiges annotiertes Datensatz und eine Open-Source-Pipeline sind unter \url{https://github.com/notsofun/Master_Thesis} verfügbar.

    \end{otherlanguage}

\end{abstract}

\newpage

\end{document}