% ADD THIS HEADER TO ALL NEW CHAPTER FILES FOR SUBFILES SUPPORT

% Allow independent compilation of this section for efficiency
\documentclass[../CLthesis.tex]{subfiles}

% Add the graphics path for subfiles support
\graphicspath{{\subfix{../images/}}}

% END OF SUBFILES HEADER

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% START OF DOCUMENT: Every chapter can be compiled separately
\begin{document}

\phantomsection% to get the hyperlinks in PDF) right
\addcontentsline{toc}{chapter}{Acknowledgment}
\chapter*{Acknowledgment}

I would like to express my sincere gratitude to my supervisor, Prof. Dr. Gerold Schneider. Throughout the writing of this thesis, his dedicated and responsible guidance kept my research on track. His precise and valuable advice, particularly his professional judgment during literature review and dataset construction, saved me from wasting time on immature ideas. His suggestion to utilize high-resource languages and established pipelines was a major inspiration that significantly improved the results of this study.

I am also grateful to Janis Goldzycher for the methodological inspiration. He helped me realize that my analysis should be grounded in clear computational formulas rather than staying at a conceptual level.

On the experimental side, I would like to thank the open-source communities such as Hugging Face and GitHub for providing excellent model weights and datasets. I also thank the AutoDL platform for providing affordable computing resources, which ensured the smooth execution of training and inference.

Finally, I want to thank my family. Your silent support allowed me to complete my studies in Zurich, thousands of miles away from home, and achieve a breakthrough in my career path. To my friends in Zurich, China, and the Americas—whether you were by my side or across the ocean—your companionship kept me optimistic through every academic challenge.

Reflecting on this work, the core logic actually aligns with the quantitative methods I used during my undergraduate studies (using KH Coder for Classical Chinese). However, during this Master's program, I successfully transitioned from being a ``user" of frameworks to a ``developer." Instead of just following existing metrics, I was able to build new quantitative pipelines based on my own qualitative hypotheses. This evolution was exactly my goal in choosing to study Computational Linguistics.

Moving forward, I will start my career as an AI Infrastructure Solution Engineer. I hope to apply the technical and humanistic knowledge gained during this research to serve as a solid bridge that helps business development run more smoothly.

Thank you all once again, and I wish everyone a successful 2026!

\newpage

\end{document}