% ADD THIS HEADER TO ALL NEW CHAPTER FILES FOR SUBFILES SUPPORT
\documentclass[../CLthesis.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}
% END OF SUBFILES HEADER

\begin{document}

\chapter{Conclusion}%
\label{chap:conclusion}

This thesis set out to demonstrate that cross-lingual hate speech analysis need not remain trapped in the binary, English-centred paradigm that has dominated the field. By combining multilingual Transformer representations with a structured explanatory framework --- unsupervised thematic discovery, target identification, attack-frame classification, and moral-axis projection --- it has shown that implicit, complex religious hostility can be deconstructed in principled ways across typologically distant languages. The chapters that follow present those demonstrations in detail. This concluding chapter steps back from the data and asks what has been learned at the level of scientific principle, what value that knowledge carries beyond the specific case of anti-Christian hate speech, and what the present study cannot claim.

% ------------------------------------------------------------------
\section{Revisiting the Core Motive and Conclusive Statement}
\label{sec:conclusion-motive}
% ------------------------------------------------------------------

Current hate speech research suffers from a double narrowness: it is concentrated on a handful of high-resource target categories (antisemitism, Islamophobia, and misogyny in English), and it frames detection as a binary classification problem that collapses structured hostility into a single label. As a consequence, the field has little to say about how hostility is organised, who exactly is targeted, or why speakers in different cultural contexts direct antagonism toward the same institution in structurally different ways.

This thesis has confirmed, across a corpus spanning three typologically and culturally distinct languages, that both narrownesses can be overcome. The evidence assembled across seven empirical chapters establishes that it is feasible to cross language barriers without translation-based mediation --- using cross-lingual centroid alignment on multilingual embeddings --- and to decompose anti-Christian hostility into interpretable dimensions that serve social-scientific inquiry rather than benchmark optimisation alone. The research questions posed in Chapter~\ref{chap:intro} have received substantive answers: the corpus yields a clear picture of who is targeted (and how target structures differ by language community), how hatred is expressed (through genre-like rhetorical conventions tied to target type), and why people hate (through moral motivation profiles that diverge fundamentally between English and East Asian discourse). The central thesis is thereby confirmed: combining multilingual Transformer representations with a structured explanation framework makes it possible to conduct fine-grained, cross-lingual analysis of implicit religious hostility at a scale and resolution that prior methods could not achieve.

% ------------------------------------------------------------------
\section{Core Scientific Discoveries}
\label{sec:conclusion-discoveries}
% ------------------------------------------------------------------

Setting aside the specific measurements reported in earlier chapters, three findings possess generality that extends beyond the anti-Christian case.

\textbf{Discovery 1: Cross-lingual hate speech is governed by genre-like rhetorical conventions, not by undifferentiated emotional output.}
The attack-frame analysis reveals that frame selection is systematically determined by target category rather than by language or speaker identity. Clerical role targets consistently attract the Sexual Abuse Frame across all three language communities; collective identity labels attract Rhetorical Attack and Moral Accusation; institutionally-embedded targets in Japanese attract Political Interference and Economic Exploitation. This regularity --- stable across languages whose rhetorical traditions are otherwise quite different --- implies that hate speech operates according to target-contingent scripts. The implication for detection is direct: models that collapse all attacks into a single hostility label discard the most informative structural signal in the data.

\textbf{Discovery 2: English and East Asian communities inhabit structurally different rhetorical modes of anti-Christian hostility.}
The moral-axis projection reveals a fundamental paradigm divergence that would be invisible to purely lexical analysis. English-language discourse aligns negatively across the full set of classical Moral Foundation axes simultaneously, constituting a broad moral condemnation of Christianity for alleged failures within a shared Anglophone ethical framework. Chinese and Japanese discourse, by contrast, aligns positively on those classical foundations but negatively on the Symbolic Threat and Realistic Threat axes, framing Christianity as an external danger to cultural identity and social cohesion rather than as an internal moral violator. This East Asian versus Western divide in the moral architecture of religious hostility is not a surface-level linguistic difference; it reflects a deeper divergence in the cultural scripts through which collective antagonism is constructed and legitimised.

\textbf{Discovery 3: Unsupervised topic modelling reveals a structured discourse landscape rather than a collection of isolated grievances.}
BERTopic processing of the full trilingual corpus identified 47 coherent topics, which further organise into a small number of interpretable discourse domains. The most prominent domain is the intersection of religion and public politics: the Unification Church--LDP nexus, the entanglement of Catholic identity with electoral choices and abortion debates, and the politicisation of religious immigration in the Canadian context together constitute the single largest thematic field in the corpus. A second domain covers gender, sexuality, and family ethics --- spanning LGBTQ+ recognition, women's ordination, and sacramental law --- and is notably the most cross-linguistically balanced, indicating that these debates reproduce across all three communities in structurally parallel ways. A third domain addresses intra-church authority and reform, including clerical abuse accountability and theological conservative-versus-liberal polarisation. The fact that unsupervised analysis converges on these three coherent domains rather than producing fragmented noise validates the thematic scaffolding approach and demonstrates that online anti-Christian discourse is not random hostility but a structured argumentative landscape.

% ------------------------------------------------------------------
\section{Multi-Dimensional Implications}
\label{sec:conclusion-implications}
% ------------------------------------------------------------------

\textbf{Engineering and practical implications.}
The components developed in this thesis --- the domain-specific trilingual gazetteer, the ten-class attack-frame taxonomy, and the LLM-assisted back-translation augmentation strategy --- are not artefacts tied to Christianity. Each is designed as a substitutable module: the gazetteer can be repopulated with target entities from another domain, the frame taxonomy can be adapted to a different attack typology, and the augmentation pipeline is agnostic to the ideological content of the source texts. Together, they constitute a modular toolkit for low-resource, cross-lingual social media content analysis that can be adopted without redesigning the underlying architecture. The complete codebase has been released as open-source software at \url{https://github.com/notsofun/Master_Thesis}, enabling other researchers and practitioners to replicate the pipeline, extend it to new target domains, or integrate individual components into existing content-moderation workflows.

\textbf{Cognitive and sociological implications.}
This thesis substantially extends the empirical foundation of computational religious hate speech research. Prior corpus-based work has overwhelmingly focused on antisemitism and Islamophobia; anti-Christian hostility, despite its global reach and cross-linguistic presence, has attracted almost no systematic computational attention. The trilingual corpus assembled here, together with the annotated target, frame, and moral-axis layers derived from it, provides a new empirical resource for understanding digital-era transnational cultural conflict. The discovery that English and East Asian communities do not share the same moral architecture of religious hostility --- even when directing antagonism toward the same institution --- has direct relevance for sociological accounts of how globalisation shapes collective antagonism, and for platform policy that often assumes a single universal hostility profile. The dataset, together with instructions for access and replication, is documented in the repository README at \url{https://github.com/notsofun/Master_Thesis}.

% ------------------------------------------------------------------
\section{Macro-Limitations and Future Directions}
\label{sec:conclusion-limitations}
% ------------------------------------------------------------------

The conclusions drawn above are bounded by two structural limitations that belong to the level of research design rather than model performance.

\textbf{Limitation 1: The cross-sectional corpus cannot capture discourse dynamics.}
The corpus lacks the high-precision timestamps that would be needed to trace how specific triggering events reshape the discourse landscape over time. The Unification Church--LDP nexus, for example, almost certainly underwent a dramatic discursive shift in the immediate aftermath of the July 2022 assassination; the current corpus can document that this nexus is quantitatively dominant, but it cannot characterise the temporal trajectory of that dominance. The moral motivation profiles reported in Chapter~\ref{chap:moral} reflect structural distributions across the full corpus, not dynamic processes of discourse formation and decay. Future work should incorporate interrupted time-series analysis, tracking shifts in moral vocabulary and frame distributions across precisely dated intervals surrounding identifiable crisis events. Such an approach would make it possible to distinguish stable ideological commitments from event-triggered discourse mobilisation --- a distinction that is analytically important but invisible in cross-sectional data.

\textbf{Limitation 2: Keyword-based corpus construction systematically excludes implicit hostility.}
The retrieval strategy that built the corpus --- keyword matching on explicit religious terms --- is designed to capture the lexically visible portion of anti-Christian discourse. Hostility expressed without triggering those keywords, whether through oblique reference, irony, or code-switching, is systematically absent from the analysis. The picture presented here is therefore a picture of explicit, surface-visible antagonism; the full discourse ecology extends considerably further into registers that the current pipeline cannot access. Future work should explore cross-lingual prompt-based retrieval strategies that are not anchored to predefined keyword vocabularies, and should test whether the who--how--why framework generalises to other hate speech domains --- racial, ethnic, and political hostility --- where implicit expression is often the dominant mode. Such transfer experiments would both extend the reach of the current framework and provide a principled test of its generalisability.

These limitations do not undermine the contributions documented above, but they make clear that the present study opens a research programme rather than closes one. The evidence that cross-lingual transformer methods can yield structured, interpretable accounts of religious hostility across Chinese, Japanese, and English establishes a foundation from which temporally-aware and keyword-free extensions become tractable next steps.

\subfilebibliography
\end{document}
