% ADD THIS HEADER TO ALL NEW CHAPTER FILES FOR SUBFILES SUPPORT
\documentclass[../CLthesis.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}
% END OF SUBFILES HEADER

\begin{document}
\chapter{Discussion}%
\label{chap:discussion}

The preceding three empirical chapters addressed the three research questions of this thesis in sequence: who is targeted in anti-Christian online hate speech (Chapter~\ref{chap:who}), how that hostility is rhetorically expressed (Chapter~\ref{chap:how}), and what moral motivations underlie it across language communities (Chapter~\ref{chap:why}). This chapter synthesises those findings into a coherent cross-lingual account, situates them in relation to the theoretical frameworks and prior work introduced in Chapter~\ref{chap:related-work}, examines the socio-political contexts that explain the patterns observed, and critically evaluates the analytical pipeline developed in Chapter~\ref{chap:methods}. The chapter closes with a discussion of practical implications for platform governance and directions for future research.

% ------------------------------------------------------------------
\section{Synthesis: The Structured Logic of Anti-Christian Hate Speech}
\label{sec:discussion-synthesis}
% ------------------------------------------------------------------

Taken together, the empirical findings of this thesis reveal that anti-Christian hate speech is not an undifferentiated expression of hostility but a structured discursive practice, organised along consistent lines of target selection, rhetorical strategy, and moral justification. The three research questions were designed to peel back successive layers of this structure, and the results across all three layers converge on a coherent picture.

At the level of targets (RQ1), the analysis confirmed that there exists a shared transnational core to anti-Christian discourse. Jesus appears as the most frequently targeted individual in both English (209 mentions) and Chinese (201 mentions), and Catholic institutional categories are prominent across all three language communities. The cross-lingual brainwashing metaphor --- EN: \textit{brainwashed}; ZH: 洗脑; JA: 洗脳 --- further attests to the existence of shared cognitive frames that operate across linguistic and cultural divides. Yet this shared core is embedded in strikingly divergent target structures. English targeting is broad and identity-anchored, distributing attention across theological figures, clerical role categories, collective identity labels, and contemporary political actors such as Trump. Chinese targeting concentrates on the clerical hierarchy and institutional structures of the Church (教会: 306 mentions, the single highest count across the entire dataset), framed through a register that foregrounds deception and exploitation, as captured by the distinctive pejorative 神棍 (\textit{religious fraudster}). Japanese targeting is almost entirely absorbed by a single politically-situated narrative: 統一教会 (Unification Church, 473 mentions) paired with 安倍晋三 (Shinzo Abe, 92) and 自民党 (Liberal Democratic Party, 59), transforming religious hostility into a vehicle for domestic political critique.

At the level of attack frames (RQ2), the findings reveal that frame selection is not random but systematically shaped by the social category of the target. Across all three language communities, clergy targets attract the Sexual Abuse Frame as their dominant mode of attack (priests in English: 50\% of predicates; 神父 in Chinese: 55\%); collective identity labels attract Rhetorical Attack and Moral Accusation; and the distinctive Japanese target pair of Unification Church and LDP attracts Political Interference and Economic Exploitation. This target-to-frame alignment reveals an underlying logic: the attacker selects the target, deploys the rhetorical weapon appropriate to that target's social role, and grounds the attack in the moral values that make it compelling within their specific discursive community.

At the level of moral motivations (RQ3), the most significant finding is the fundamental divergence in the moral vocabulary deployed across language communities. English-language discourse is negatively aligned across all five classical Moral Foundations axes simultaneously --- Harm, Fairness, Loyalty, Authority, and Sanctity --- constituting what might be described as a comprehensive moral condemnation: Christianity is attacked as broadly failing multiple ethical standards at once. Chinese and Japanese discourse, by contrast, show positive alignment on the classical foundations but flip sharply negative on the Symbolic Threat and Realistic Threat axes. The implied accusation in these settings is not that religion has failed morally in a universal sense, but that it constitutes a danger to cultural identity, social cohesion, or material security. Anti-religious hate speech in all three communities is, in the formulation of the RQ3 analysis, a moral argument rather than a simple expression of dislike. What changes across languages is which moral charge is invoked --- and that choice, as the following sections demonstrate, is far from arbitrary.

% ------------------------------------------------------------------
\section{Theoretical Contributions}
\label{sec:discussion-theory}
% ------------------------------------------------------------------

The findings of this thesis speak to several theoretical debates in the study of hate speech and its computational analysis.

\subsection{Beyond Detection: The Internal Structure of Hateful Discourse}

The dominant paradigm in computational hate speech research frames the task as binary classification: identifying whether a text is hateful or not \citep{jahan_systematic_2023, ramos_comprehensive_2024}. The present findings reinforce the argument, advanced by \citet{matamoros-fernandez_racism_2021} and others, that this framing forecloses the very questions that matter most for sociological analysis. The who-how-why pipeline demonstrates that hate speech possesses an internal three-layer structure --- target, rhetorical form, and moral motivation --- that a detection-only approach cannot recover. The finding that attack frame selection is determined by target category (Section~\ref{sec:rq2-by-target}) is particularly significant: it shows that hateful discourse is produced according to genre-like regularities, in which different social roles attract different modes of attack. A binary label cannot capture this regularity, nor can it support the kind of comparative social analysis that identifies what is similar and what is distinctive across languages.

This contribution extends \citet{ollagnier_unsupervised_2023}'s unsupervised clustering approach, which successfully identifies topical structures in hate speech but stops short of providing a structured interpretive account of the discourse's rhetorical and moral logic. By building a sequential pipeline in which clustering supplies the thematic scaffold for frame and motivation analysis, the present thesis demonstrates how computational grouping and structured sociological interpretation can be integrated rather than treated as separate tasks.

\subsection{Intergroup Threat Theory Extended to Religious Symbols}

Classical applications of Intergroup Threat Theory \citep{stephan2000integrated} have focused primarily on racial, ethnic, and immigration contexts, modelling hostility as a response to the perceived threat posed by an outgroup to the material resources or cultural values of an ingroup. The present findings extend this framework to the domain of religious hate speech, and specifically to the East Asian case in which Christianity functions as a symbolically foreign institution rather than a majority religion.

The RQ3 results provide direct empirical support for this extension. The negative alignment of Chinese and Japanese discourse on the Symbolic Threat axis --- indicating that the discourse frames Christianity as a danger to cultural identity and social cohesion --- is precisely what Intergroup Threat Theory predicts when a minority religion is positioned as a civilisational outsider. The Japanese case additionally exemplifies Realistic Threat: the Unification Church is attacked not primarily on theological grounds but as an organisation that has materially penetrated and distorted domestic political processes (Political Interference, Economic Exploitation frames). The Church's foreign origin (韓国, South Korea, appearing in the Japanese top-20 targets) is invoked to amplify the threat narrative, encoding institutional critique as civilisational suspicion.

Importantly, this pattern does not obtain in English, where the Realistic Threat axis is the only one that remains positive, and Christianity is attacked as an institution that has failed morally within a context where it remains culturally dominant. This contrast supports the theoretical prediction that threat-based hostility is specifically activated when the target group is perceived as an external agent rather than an internal moral failure. The present study thus shows that ITT can be productively extended beyond race and immigration to analyse how religious symbols are positioned as threats in digitally mediated discourse.

\subsection{Moral Foundations Theory and Cross-Lingual Activation Patterns}

Moral Foundations Theory \citep{graham2009liberals, haidt2012righteous} proposes that moral intuitions are universally organised along five fundamental dimensions. The present findings do not challenge this universalism, but reveal systematic cross-cultural variation in which foundations are activated in the specific context of religious hate speech. The English ``moral condemnation bundle'' --- in which all five foundations are simultaneously negative --- suggests a discourse strategy of comprehensive ethical indictment: Christianity is argued to be harmful, unfair, corrupt, disloyal, and impure, all at once. The East Asian ``threat-dominant'' pattern, in which the classical foundations remain relatively positive while the Threat axes turn sharply negative, reflects a different rhetorical logic: the moral charge is not that the religion has done something wrong within a shared ethical framework, but that it is incompatible with the ingroup's cultural and social framework.

This distinction has implications for how hate speech is theorised. The English profile is consistent with what might be called an \emph{immanent critique}: the attackers share, or at least invoke, a common moral vocabulary with the broader culture, and argue that the religion has violated it. The East Asian profile is closer to an \emph{exclusionary framing}: the attack is grounded less in shared moral standards and more in a logic of cultural non-belonging. These two rhetorical strategies are likely to require different interpretive frameworks and different moderation responses, a point elaborated in Section~\ref{sec:discussion-implications}.

\subsection{Implicit Hate Speech in a Multilingual Setting}

The analysis of attack frames (RQ2) provides substantial evidence that the most prevalent forms of anti-Christian hate speech in this corpus are implicit rather than explicit. The Sexual Abuse Frame in Chinese --- lexically realised through 性侵 (\textit{sexual assault}), 丑闻 (\textit{scandal}), and 猥亵 (\textit{molestation}) --- and the Political Interference frame in Japanese --- realised through 支配 (\textit{domination}), 選挙 (\textit{election}), and 献金 (\textit{donations}) --- both operate through narrative allegation rather than slurs or explicit dehumanisation. A detector trained on explicit markers would miss the bulk of the hostile content identified in this corpus.

This finding confirms and extends \citet{elsherief_latent_2021}'s account of latent hate speech, demonstrating that implicit framing patterns are not specific to English but a structural feature of online religious hate speech across languages. The cross-lingual finding that Dehumanisation vocabulary is sparse in English but more developed in Chinese (毒瘤, \textit{malignant tumour}; 干掉, \textit{eliminate}) and Japanese (ゴキブリ, \textit{cockroach}) further complicates the assumption that explicit dehumanisation is the primary severity marker across cultural contexts.

% ------------------------------------------------------------------
\section{Socio-Cultural Contextualisation}
\label{sec:discussion-context}
% ------------------------------------------------------------------

The divergent target profiles, frame repertoires, and moral motivation signatures of the three language communities are not statistical artefacts. They reflect the specific contemporary social and political circumstances within which each community produces anti-religious discourse. Interpreting the findings without this contextual grounding would risk reducing structural patterns to pseudo-universals.

\subsection{Japan: Religion as Political Indictment}

The near-total dominance of Topic~0 in the Japanese corpus, and the associated concentration of targets on 統一教会, 安倍晋三, and 自民党, is a direct reflection of the most consequential political event in Japan in a generation. The assassination of former Prime Minister Shinzo Abe in July 2022 prompted an extended public reckoning with the Liberal Democratic Party's decades-long financial and electoral relationship with the Family Federation for World Peace and Unification (Unification Church), a relationship that had remained largely hidden from public scrutiny. The scandal exposed a pattern in which individual politicians used Church networks for canvassing while the organisation benefited from political protection against regulatory oversight \citep{mullins2021religion}.

In this context, the Unification Church became a lightning rod for accumulated public frustration with the conservative political establishment. Anti-religious discourse in Japanese is therefore best understood not as theological controversy but as displaced political critique: the religious organisation is attacked as the embodiment of structural corruption, foreign influence, and the betrayal of democratic accountability. This contextualisation explains several structural features of the Japanese findings simultaneously: the dominance of Political Interference and Economic Exploitation frames, the high proportion of Political Group targeting, the appearance of 韓国 (South Korea) in the target list encoding the Church's foreign origin as part of the critique, and the threat-based moral profile that frames the organisation as dangerous to social cohesion rather than simply immoral.

\subsection{China: Secular Pragmatism and the Critique of Western Institutions}

Chinese anti-Christian discourse reflects a different contemporary configuration. The concentration of the Sexual Abuse Frame (26\% of predicates) and Institutional Rot vocabulary (包庇, \textit{cover-up}; 官官相护, \textit{officials shielding each other}) aligns with a broader pattern in Chinese internet culture: a secular, pragmatist worldview that is sceptical of Western moral authority and finds in clerical scandal a powerful empirical confirmation of its critique. The distinctive pejorative 神棍 (\textit{religious fraudster/charlatan}) is particularly revealing: it frames clergy not as misguided believers but as deliberate impostors who exploit the faithful's trust for personal gain, a framing entirely consistent with an anti-clerical register grounded in suspicion of institutional hypocrisy rather than theological disagreement.

The Symbolic Threat dimension of the RQ3 findings adds a further layer. Chinese online discourse frames Christianity not only as institutionally corrupt but as culturally incompatible: clerical scandals become evidence not merely of individual or institutional failure but of the fundamental foreignness of Western religion. This rhetorical move --- transforming particular misconduct into civilisational critique --- reflects the broader dynamics of Chinese internet nationalism, in which Western cultural institutions are systematically positioned as threats to social cohesion and national identity \citep{yang2011religion}. The pipeline's finding that Chinese discourse is negatively aligned on cultural cohesion (Symbolic Threat) while remaining relatively normative on the classical moral foundations is consistent with this interpretation: the problem with Christianity, in this discursive register, is not that it violates universal moral standards but that it does not belong.

\subsection{English: Culture Wars and the Moral Failure of Majority Religion}

English anti-Christian discourse operates in a structurally different setting. In predominantly English-speaking contexts, Christianity remains a culturally influential majority institution, and hostility accordingly takes the form of resistance to majority power rather than suspicion of a foreign minority organisation \citep{Yancey2014, scheitle2020}. The co-presence of Trump (94 mentions) alongside Jesus (209) and Catholic institutional targets reflects the deeply politicised character of Anglophone religious discourse in the post-2016 period. Christian identity has been instrumentalised by right-wing populism --- most explicitly through the discourse of Christian nationalism --- in ways that generate sustained counter-mobilisation from secular, progressive, and LGBTQ+ communities. The high proportion of LGBTQ+ and \textit{Catholic teaching} discourse in Topic~3, and the concentration of condemnation-oriented moral framing in Topics involving gender and politics, reflects this cultural context directly.

The broad negative profile across all five Moral Foundations axes (Section~\ref{sec:rq3_lang}) is the quantitative signature of this comprehensive indictment: it is not one specific moral failure that is being targeted but the entire moral ecology of institutionalised Christianity --- its complicity in sexual abuse, its resistance to gender equality, its entanglement with political power, and its claims to moral authority over public life. The relative positivity of the Realistic Threat axis in English (the only language where this axis is positive) is consistent with the structural position of Christianity in these settings: it is experienced as a moral actor that has failed, not as an external threat to cultural identity.

% ------------------------------------------------------------------
\section{Pipeline Evaluation: Affordances and Limitations}
\label{sec:discussion-pipeline}
% ------------------------------------------------------------------

A stated objective of this thesis is to develop an interpretable, reusable analytical pipeline that can serve as a template for computational social-scientific inquiry into hate speech. Having reported the substantive findings, it is necessary to assess the pipeline's performance honestly --- both what it does well and where its design choices introduce limitations that constrain the conclusions that can be drawn.

\subsection{Affordances: What the Pipeline Does Well}

The modular, sequential architecture of the pipeline (BERTopic~$\to$~RQ1~$\to$~RQ2~$\to$ \allowbreak ~RQ3) offers several genuine strengths. The cross-lingual centroid alignment procedure, applied before the UMAP and HDBSCAN clustering steps, enabled effective multilingual topic formation without translation: the cross-lingual fusion rate achieved in BERTopic provides validation that Chinese, Japanese, and English documents on shared themes are grouped together rather than into separate language silos. This is a non-trivial achievement for a corpus spanning three structurally distinct writing systems.

The three-layer target extraction design for RQ1 (spaCy NER~$\to$~domain gazetteer~\allowbreak $\to$~Gemini LLM fallback) was specifically motivated by a structural challenge that simpler approaches cannot address: zero-subject constructions and topic-drop are grammatically normal in both Chinese and Japanese, meaning that many sentences targeting a religious entity do so without an explicit subject or object that dependency-based NER can detect. The LLM fallback recovered targets in precisely the structurally incomplete sentences where Stage~1 and Stage~2 would otherwise produce null results, ensuring coverage of a segment of the corpus that is analytically important for any study of implicit hate.

Similarly, the three-layer predicate extraction for RQ2 (dependency parsing~$\to$~predicate window~$\to$~LLM frame classification) was designed to handle the diversity of syntactic structures across social media text in three languages. The complementary layering strategy --- using dependency parsing where full SVO structure is available and predicate windowing where it is not --- provides broader coverage than either method alone.

At the level of RQ3, the FrameAxis projection approach \citep{Kwak_2021} offers an important advantage over supervised annotation: it does not require a labelled training set for moral motivation, which would be prohibitively expensive to construct across three languages. By constructing axis vectors from multilingual moral dictionaries and projecting documents onto those axes via cosine similarity, the pipeline produces morally interpretable outputs at the scale of the full corpus while remaining grounded in established theoretical frameworks.

Finally, the pipeline's overall design is reusable: the gazetteer, frame taxonomy, and prompt templates are not hard-coded to Christianity but can be adapted to other hate speech targets by substituting domain-appropriate lexicons and category definitions. This modularity supports the thesis's claim to a methodological contribution beyond the specific empirical case.

\subsection{Data Limitations: Corpus Construction and Coverage}

The corpus was constructed using keyword-based queries on social media platforms. This introduces a systematic selection bias: the pipeline captures only texts that employ explicit surface markers of anti-Christian content. Hate speech that avoids these markers --- for example, discourse that attacks Christianity through irony, allusion, or contextually coded language without using identifiable keywords --- is excluded from the corpus by construction. This means that the prevalence and variety of implicit hate speech is likely underestimated relative to its actual occurrence in online discourse, and the frame and motivation profiles reported in Chapters~\ref{chap:how} and~\ref{chap:why} should be understood as characterising the portion of anti-Christian discourse that is lexically legible to a keyword filter, not the full population of such discourse.

A further data limitation concerns the fine-tuning procedures applied to improve detection in Chinese and Japanese settings. Models fine-tuned on back-translated data introduce translation artefacts that may not fully capture the idiomatic register, coded language, and culturally specific irony that characterise Chinese and Japanese online discourse. These artefacts could affect the composition of the corpus in ways that are difficult to detect post hoc.

\subsection{Clustering Stability and Noise Handling}

The BERTopic pipeline assigns documents that do not fit cleanly into any cluster the noise label $-1$, and these documents are excluded from downstream analysis \citep{grootendorst_bertopic_2022}. The noise ratio in the present corpus falls within the targeted range of 10--40\%, but the excluded documents may contain analytically consequential content: borderline hate speech, ambiguous sarcasm, and transitional discourse that straddles topic boundaries. The decision to exclude noise is methodologically principled but introduces a blind spot in the analysis.

The clustering solution is also sensitive to hyperparameter choices. The 47-topic solution produced by the combination of UMAP (\texttt{n\_neighbors=30}, \texttt{min\_dist=0.0}) and HDBSCAN (\texttt{min\_cluster\_size=20}, \texttt{epsilon=0.05}) represents one configuration in a space of possible solutions. Topics at the margin of the chosen parameterisation may split or merge under alternative settings, which could affect the topic-level frame and motivation profiles. A systematic sensitivity analysis across hyperparameter ranges was not conducted and remains an open question for replication.

\subsection{LLM Reliability and Reproducibility}

Both the target identification fallback (RQ1) and the frame classification (RQ2) rely on Gemini API calls, introducing non-determinism into the pipeline. Rerunning the analysis with different random seeds or at different times may produce slightly different target lists and frame assignments, because LLM outputs are not fully deterministic even with temperature set to zero. The frame classification prompt was developed iteratively through pilot testing rather than validated against a formally constructed held-out annotation set, meaning that the reported frame distributions reflect the model's interpretation of the taxonomy rather than a gold-standard human judgement. Estimated inter-rater agreement between the LLM and a human annotator on a random sample of classified predicates would strengthen confidence in the frame-level results; this constitutes a limitation of the current study.

Rate limiting and API quota constraints additionally prevented multiple independent runs of the LLM-intensive pipeline stages, precluding a systematic assessment of output variance across runs. Future implementations should incorporate caching and multi-run comparison as standard components of the validation process.

\subsection{FrameAxis: Epistemological Constraints and Dictionary Coverage}

The moral motivation analysis in RQ3 carries two epistemological constraints that deserve explicit acknowledgement. The first is the cross-sectional nature of the corpus. Because the texts were collected without high-resolution timestamps enabling event-level linkage, the analysis cannot track how specific real-world events function as triggers for moral framing shifts. The assassination of Shinzo Abe, the emergence of individual clerical abuse cases, and shifts in political discourse around Christian nationalism all represent external catalysts (causes) that are likely to have shaped the moral vocabulary present in the corpus (effects). What the FrameAxis analysis measures is the structural distribution of moral vocabularies across the corpus, rather than the dynamic process by which those vocabularies are activated. This is an appropriate and defensible research design for a study whose primary interest is discourse structure rather than event causality, but it means that causal inferences about what drives moral framing remain beyond the scope of the evidence.

The second constraint concerns dictionary coverage. The Chinese Moral Foundations Dictionary \citep{cheng_c-mfd_2023} does not provide explicit virtue/vice polarity annotations; polarity was inferred using negation-prefix rules, a procedure that may misclassify compound terms or words whose moral valence is context-dependent. The J-MFD \citep{matsuo2019development} was developed for general Japanese text and may not fully capture the register of online political discourse, particularly the specialised vocabulary associated with the Unification Church scandal. Both dictionaries are likely to underrepresent the colloquial and politically coded language that is characteristic of social media, introducing an upward bias in axis scores for topics whose hostility is expressed through neologisms and coded terms not present in the dictionary vocabulary.

Finally, the high empirical correlation among the five classical Moral Foundations axes within the corpus (pairwise $r \approx 0.8$, as reported in Chapter~\ref{chap:why}) limits the ability to distinguish individual moral foundations analytically. The analysis accordingly treats them as a single moral condemnation bundle and focuses on the Threat axes as the primary differentiating dimensions. This is a principled response to the data structure, but it means that the fine-grained theoretical distinctions among Harm, Fairness, Loyalty, Authority, and Sanctity --- distinctions that are meaningful in survey-based MFT research \citep{graham2009liberals} --- cannot be reliably maintained in this corpus. Future work using purpose-built, platform-specific moral lexicons with validated polarity annotations could recover this granularity.

% ------------------------------------------------------------------
\section{Practical Implications}
\label{sec:discussion-implications}
% ------------------------------------------------------------------

The findings of this thesis have direct implications for how online hate speech involving religious communities is detected, classified, and moderated in practice.

\subsection{The Inadequacy of Lexical Detection for Frame-Based Hate}

The most consistent practical lesson from this study is that lexical or keyword-based content moderation is insufficient for the forms of anti-Christian hate speech most prevalent in this corpus. A moderation system that flags explicit slurs will catch a small minority of the hostile content identified here: it will detect 基督狗 but not the Sexual Abuse Frame constructed through 性侵/丑闻/猥亵 co-occurring with clerical role targets; it will detect 洗脳 but not the Political Interference frame built around 支配/選挙/献金 applied to the Unification Church and LDP. The finding that Rhetorical Attack is the dominant frame across topics in all three languages further suggests that much anti-religious hostility operates through sarcasm and critical invective that resist lexical operationalisation.

This is precisely the structural feature of implicit hate speech that \citet{elsherief_latent_2021} identified as the frontier challenge for automated moderation. The present study extends that diagnosis to a multilingual religious context and provides a concrete account of which frames are most prevalent in each language community, offering a target for frame-aware detection system development.

\subsection{Language-Specific Moderation Strategies}

The three language communities engage distinct frame repertoires, and effective moderation strategies should be calibrated accordingly. In Japanese-language contexts, the primary challenge is distinguishing coordinated anti-Unification Church discourse --- which combines legitimate political commentary on Church-LDP ties with genuinely hateful content targeting believers and vulnerable populations financially exploited by the organisation --- from the broader class of political criticism. A moderation system sensitive to the co-occurrence of 献金 (donation), 詐欺 (fraud), 搾取 (exploitation), and 統一教会 within a single post, combined with targeting of lay 信者 (\textit{believers}) rather than institutional actors, is better positioned to identify harmful rather than merely political content.

In Chinese-language contexts, the concentration of the Sexual Abuse Frame on clerical role targets calls for pattern-level rather than token-level detection. The cover-up vocabulary cluster (包庇, 官官相护) co-occurring with clergy role labels (神父, 主教, 教皇) is a more reliable signal of coordinated institutional attack than any individual term. Identifying this pattern requires dependency-level or co-occurrence-based features rather than simple keyword lists.

In English-language contexts, the breadth of the moral condemnation profile and the dominance of Rhetorical Attack as the frame of choice present a different challenge: distinguishing legitimate religious critique, which is a protected form of expression, from targeted harassment of individuals or coordinated dehumanisation of communities. Frame-level classification --- identifying not just the presence of hostile content but its specific rhetorical structure and target --- provides the granularity needed to support such distinctions.

\subsection{From Binary Moderation to Structured Diagnosis}

More broadly, the who-how-why framework suggests a reframing of the automated moderation task. Rather than returning a binary label, a moderation-oriented application of the pipeline would return a structured diagnostic report specifying the target (who is attacked), the attack frame (how the attack is constructed), and the moral motivation (what justificatory logic sustains it). This structured output would support more precise human review decisions, enable more informative appeals processes, and provide platform researchers with interpretable data on which forms of hate speech are most prevalent in their communities at a given time.

This reframing aligns with recent calls in the research community for more explainable and socially grounded moderation systems \citep{mathew_hatexplain_2021}. It also reflects the thesis's foundational commitment: the goal is not to build a more accurate classifier, but to develop an interpretive framework that makes the structure of hate speech legible to social analysis and, ultimately, to governance.

\subsection{Directions for Future Research}

Several directions follow directly from the limitations identified in Section~\ref{sec:discussion-pipeline}. First, the cross-sectional constraint of the present corpus motivates the development of a longitudinal variant of the pipeline in which high-resolution timestamps enable interrupted time-series analysis. Applying the FrameAxis projection model to corpus segments corresponding to periods before and after specific triggering events --- such as the Abe assassination for the Japanese corpus --- would allow researchers to measure how real-world catalysts shift the moral axis profiles of online discourse, closing the explanatory gap between discourse structure (what the present study measures) and event causality (what it cannot directly address).

Second, the dictionary coverage limitations motivate the construction of platform-specific, register-adapted moral lexicons for Chinese and Japanese online discourse. Corpus-derived lexicons built from social media text, with polarity validated through human annotation, would replace the approximations introduced by applying general-language dictionaries to an online-specific corpus and enable more reliable axis-level comparisons across MFT foundations.

Third, the frame classification step would benefit from a formal inter-rater reliability study comparing LLM-assigned labels with human annotations on a held-out sample, and from the development of a gold-standard benchmark dataset for attack frame classification in Chinese, Japanese, and English religious hate speech. Such a resource would enable calibrated confidence estimates for the frame distributions reported in Chapter~\ref{chap:how} and support systematic comparison across pipeline variants.

Finally, the modularity of the who-how-why framework invites application beyond anti-Christian hate speech. Replacing the religious gazetteer with target lexicons appropriate to racial, ethnic, or political hate speech, and adapting the frame taxonomy to the corresponding rhetorical repertoires, would test the framework's transferability and potentially establish it as a general-purpose template for structured hate speech interpretation across domains.

\subfilebibliography
\end{document}
